Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-03 paper/main.tex
paper table

\begin{table*}[tb]%time
\begin{tabular}{llrrrrrr}
\toprule
Problem &    Instance &  CEGO\_inv &  CEGO\_orig &  UMM\_100 &  UMM\_200 &  UMM\_400 &  UMM\_no\_inv \\
\midrule
    LOP &  N-t59b11xx &   1265.98 &    1240.36 &     1.37 &     5.78 &    22.24 &       21.89 \\
    LOP &  N-t59d11xx &   1269.93 &    1252.89 &     1.37 &     5.62 &    21.84 &       22.30 \\
    LOP &    N-p40-01 &   1195.90 &    1170.81 &     1.14 &     4.61 &    18.13 &       19.06 \\
    LOP &    N-p40-02 &   1207.24 &    1183.09 &     1.15 &     4.76 &    18.11 &       19.06 \\
    LOP &    N-p50-01 &   1391.55 &        NaN &      NaN &      NaN &    27.36 &         NaN \\
    LOP &    N-p50-02 &   1372.71 &        NaN &      NaN &      NaN &    28.36 &         NaN \\
    LOP &  N-sgb75.01 &   1994.22 &    2004.70 &     3.97 &    15.77 &    62.75 &       65.40 \\
    LOP &  N-sgb75.02 &   1995.09 &    1975.41 &     4.03 &    15.90 &    64.58 &       62.69 \\
   PFSP &       rec05 &   1099.63 &     917.81 &     0.30 &     1.14 &     4.54 &        4.53 \\
   PFSP &       rec13 &   1109.51 &    1043.08 &     0.31 &     1.07 &     4.55 &        4.50 \\
   PFSP &       rec19 &   1090.06 &    1087.38 &     0.63 &     2.59 &    10.51 &       10.35 \\
   PFSP &       rec31 &   1387.09 &    1367.26 &     1.79 &     6.90 &    27.84 &       26.91 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[tb]%fitness
\begin{tabular}{llrrrrrr}
\toprule
Problem &    Instance &   CEGO\_inv &   CEGO\_orig &   UMM\_400 &   UMM\_200 &   UMM\_100 &   UMM\_no\_inv \\
\midrule
    LOP &  N-t59b11xx &          102408.0 &           126204.0 &         114075.5 &         115941.5 &         128195.5 &            138819.5 \\
    LOP &  N-t59d11xx &           12692.2 &            30199.8 &          16662.9 &          22117.4 &          28050.4 &             42971.2 \\
    LOP &    N-p40-01 &           10496.6 &            15027.7 &          12369.1 &          13043.7 &          14459.3 &             16471.5 \\
    LOP &    N-p40-02 &           11714.7 &            15150.2 &          13160.5 &          13923.2 &          15027.7 &             16330.7 \\
    LOP &    N-p50-01 &           18197.7 &                NaN &          21161.8 &              NaN &              NaN &                 NaN \\
    LOP &    N-p50-02 &           19090.5 &                NaN &          21746.6 &              NaN &              NaN &                 NaN \\
    LOP &  N-sgb75.01 &         1893533.2 &          2095899.6 &        1992059.9 &        2011271.7 &        2074111.6 &           2111368.5 \\
    LOP &  N-sgb75.02 &         1895801.8 &          2069286.9 &        1967132.3 &        2011004.2 &        2045556.5 &           2056681.8 \\
   PFSP &       rec05 &            1276.2 &             1318.7 &           1276.3 &           1283.1 &           1300.4 &              1332.5 \\
   PFSP &       rec13 &            1992.9 &             2096.0 &           2057.8 &           2113.6 &           2134.9 &              2163.6 \\
   PFSP &       rec19 &            2264.5 &             2328.4 &           2304.8 &           2346.5 &           2392.4 &              2405.2 \\
   PFSP &       rec31 &            3415.5 &             3512.3 &           3419.3 &           3438.9 &           3511.9 &              3554.1 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}[tb]%time
\begin{tabular}{llrrrrr}
\toprule
Problem &    Instance &  CEGO\_inv &  CEGO\_orig &  UMM\_400 &  UMM\_200 &  UMM\_100 \\
\midrule
    LOP &  N-t59b11xx &   1265.98 &    1240.36 &    22.24 &     5.78 &     1.37 \\
    LOP &  N-t59d11xx &   1269.93 &    1252.89 &    21.84 &     5.62 &     1.37 \\
    LOP &    N-p40-01 &   1195.90 &    1170.81 &    18.13 &     4.61 &     1.14 \\
    LOP &    N-p40-02 &   1207.24 &    1183.09 &    18.11 &     4.76 &     1.15 \\
    LOP &    N-p50-01 &   1391.55 &        NaN &    27.36 &      NaN &      NaN \\
    LOP &    N-p50-02 &   1372.71 &        NaN &    28.36 &      NaN &      NaN \\
    LOP &  N-sgb75.01 &   1994.22 &    2004.70 &    62.75 &    15.77 &     3.97 \\
    LOP &  N-sgb75.02 &   1995.09 &    1975.41 &    64.58 &    15.90 &     4.03 \\
   PFSP &       rec05 &   1099.63 &     917.81 &     4.54 &     1.14 &     0.30 \\
   PFSP &       rec13 &   1109.51 &    1043.08 &     4.55 &     1.07 &     0.31 \\
   PFSP &       rec19 &   1090.06 &    1087.38 &    10.51 &     2.59 &     0.63 \\
   PFSP &       rec31 &   1387.09 &    1367.26 &    27.84 &     6.90 &     1.79 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[tb]%fitness
\begin{tabular}{llrrrrr}
\toprule
Problem &    Instance &   CEGO\_inv &   CEGO\_orig &   UMM\_400 &   UMM\_200 &   UMM\_100 \\
\midrule
    LOP &  N-t59b11xx &          102408.0 &           126204.0 &         114075.5 &         115941.5 &         128195.5 \\
    LOP &  N-t59d11xx &           12692.2 &            30199.8 &          16662.9 &          22117.4 &          28050.4 \\
    LOP &    N-p40-01 &           10496.6 &            15027.7 &          12369.1 &          13043.7 &          14459.3 \\
    LOP &    N-p40-02 &           11714.7 &            15150.2 &          13160.5 &          13923.2 &          15027.7 \\
    LOP &    N-p50-01 &           18197.7 &                NaN &          21161.8 &              NaN &              NaN \\
    LOP &    N-p50-02 &           19090.5 &                NaN &          21746.6 &              NaN &              NaN \\
    LOP &  N-sgb75.01 &         1893533.2 &          2095899.6 &        1992059.9 &        2011271.7 &        2074111.6 \\
    LOP &  N-sgb75.02 &         1895801.8 &          2069286.9 &        1967132.3 &        2011004.2 &        2045556.5 \\
   PFSP &       rec05 &            1276.2 &             1318.7 &           1276.3 &           1283.1 &           1300.4 \\
   PFSP &       rec13 &            1992.9 &             2096.0 &           2057.8 &           2113.6 &           2134.9 \\
   PFSP &       rec19 &            2264.5 &             2328.4 &           2304.8 &           2346.5 &           2392.4 \\
   PFSP &       rec31 &            3415.5 &             3512.3 &           3419.3 &           3438.9 &           3511.9 \\
\bottomrule
\end{tabular}
\end{table*}
